Figures

### 2019-11-04 figures/07_model-selection_40.Rmd
update model fig code for appendix dotplots

```{r fe}
cowplot::plot_grid(
cowplot::plot_grid(
  equalize_panels(
    gg_tp_fe + theme(axis.title.x = element_blank())
  ), 
  equalize_panels(
    gg_tn_fe + 
      theme(axis.text.y = element_blank(), 
            axis.title.x = element_blank())), 
  rel_widths = c(1, 0.95)),

@@

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
# setwd("figures")
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))

@@

```{r tn_re_compare, fig.height=3, fig.width=4}
# compare lakes in signif hu4s
dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
  group_by(key, signif_hu4) %>%
  mutate(median = median(value, na.rm = TRUE))

@@

```{r re}
cowplot::plot_grid(
cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
                                     plot.margin = unit(c(0,0,0,0), "cm")),
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank(), 
                                    axis.title.x = element_blank(),
                                    plot.margin = unit(c(0,0,0,0), "cm")), 
                   rel_widths = c(1, 0.9)), 
ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label), size = 5) +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm")),
ncol = 1, rel_heights = c(1, 0.05))

@@

```{r re-comparison, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = c(-0.2, 0.5)) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank()) +
  ggtitle("TN") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

>>>>

```{r fe_40}
cowplot::plot_grid(
cowplot::plot_grid(
  equalize_panels(
    gg_tp_fe + theme(axis.title.x = element_blank())
  ), 
  equalize_panels(
    gg_tn_fe + 
      theme(axis.text.y = element_blank(), 
            axis.title.x = element_blank())), 
  rel_widths = c(1, 0.95)),

@@

```{r tn_re_hu4_40, fig.width = 3.77, fig.height = 4.5}
# setwd("figures")
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))

@@

```{r tn_re_compare_40, fig.height=3, fig.width=4}
# compare lakes in signif hu4s
dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
  group_by(key, signif_hu4) %>%
  mutate(median = median(value, na.rm = TRUE))

@@

```{r re_40}
cowplot::plot_grid(
cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
                                     plot.margin = unit(c(0,0,0,0), "cm")),
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank(), 
                                    axis.title.x = element_blank(),
                                    plot.margin = unit(c(0,0,0,0), "cm")), 
                   rel_widths = c(1, 0.9)), 
ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
  geom_text(aes(x = x, y = y, label = label), size = 5) +
  theme_void() + 
  theme(plot.margin = unit(c(0,0,0,0), "cm")),
ncol = 1, rel_heights = c(1, 0.05))

@@

```{r re-comparison_40, fig.width=4}
re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = c(-0.2, 0.5)) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank()) +
  ggtitle("TN") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
